Quantifying the manageability of pollination networks in an invasion context

### 2017-10-15 paper/manuscript.Rmd
Keywords in alphabetical order
Add journal topic as keyword

**Keywords:** Network control theory, ecological networks, species importance, driver species, mutualism, management interventions

>>>>

**Keywords:** Driver species, ecological networks, management interventions, mutualism, network control theory, plant population and community dynamics, species importance
